Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-11-02 RR_manuscript/Draft_RR.Rmd
closes #260

The project OSF repository contains all the materials mentioned in this paper and can be accessed at <https://bit.ly/3AqU1ul>.
The repository holds three main OSF components (`Data`, `Teams analyses` and `Questionnaires`), and a link to the project's GitHub repository.
The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.

@@

As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
The code is available at <https://many-speech-analyses.github.io/suppl/simulations.html>, Section 2.^[Cached model outputs can be found at <https://bit.ly/3AgdHAN>.]
Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams. 
Thus in order to achieve our main goal, i.e. estimating variability among teams, we considered a minimum sample size of 10 teams as sufficient.
Given the exploratory nature of our study, however, we have sampled as many analysts as possible.
We received initial expressions of interest to participate from more than 200 analysts, though there was a substantial drop-out rate (see Section Results).

@@

The analysis teams registered for participation and each of the analysts individually answered a demographic and expertise questionnaire (`intake_form.pdf`).
A PDF version of this and all other questionnaires are available in the repository's `Questionnaires` component, at <https://bit.ly/3Cf3fdm>.
The questionnaire collected information on the analysts' current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We then requested that they answer the research question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
To do so, they were given the data generated by the experiment described in Section [The data set](#s:dataset).
Data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
These can be found in the `Data` component at <https://bit.ly/3Ahawc7>.

@@

Based on the common practices currently in place within the field, we anticipated that researchers would use multilevel regression models, thus common measurements of effect size, such as Cohen's $d$, might have been inappropriate.
Furthermore, @aczel2021 suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs. milliseconds for duration) which was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e. the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
Each \textsc{standardized model} was fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
Model refitting also constituted a way of validating the reported analyses, a step recommended by @aczel2021.
<!-- TODO: add link to refitting procedure -->
Details about the refitting procedure can be found at LINK.

@@

After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor in each reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
The outcome variable was the set of standardized effect sizes $\eta_i$.
The likelihood of $\eta_i$ was assumed to correspond to a normal distribution [@knight2000].
The analysis teams were entered as a group-level effect (i.e., `(1 | team)`, called *random effect* in the frequentist literature).
The standard errors $\text{se}_i$ were included as the standard deviation of $\eta_i$ to fit a measurement-error model, as discussed above.
We used regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\sigma_{\alpha_{\text{t}}}$ ($HalfCauchy(0, 1)$).
We fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
<!-- In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions. -->
The model did not incur any divergent transitions ($\hat{R}$ was not greater than 1) and the estimated sample sizes were sufficient.
<!-- TODO: add link to meta-model code -->
The code used to run the model can be found at <>.

@@

A normal distribution was used as the likelihood function of $\alpha_{t[i]}$.
The mean of $\alpha_{t[i]}$ was modeled on the basis of the overall intercept $\beta$ and on the coefficients of each predictor.
The numeric predictors were centered and scaled and the categorical predictors were sum coded.
We used a normal distribution with mean 0 and standard deviation 1 as the prior for the intercept and the predictors.
The model was run with the same settings as with the meta-analytic model.
<!-- TODO: add link to predictor model code -->
The code used to run the model can be found at <LINK>.

@@

The initiating authors discussed the limitations, results, and implications of the study and collaborated with the analysts on writing the final manuscript for review as a stage-2 Registered Report.
<!-- TODO: Add link to the collaborative document maybe? -->

@@

The results section is divided into three parts.
We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
Second, we report the results of the meta-analytic model, focusing on between-team and between-model variability. 
<!-- and the estimated meta-analytic effect of word combination typicality on speech acoustics.-->
Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
The research compendium of the study, containing all the code and data presented here, can be found at <https://osf.io/3bmcp/>.

@@

The question arises whether these unique analysis pipelines led to different conclusions. 
`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
Of the 104 submitted models, `r n_effects` were reported to show a statistically reliable effect (`r round(perc_effects,1)`%). 
<!-- It looks like this is on the level of critical coefficients = 170, rather than submitted models, double check -->

@@

This section deals with the meta-analytic analysis of the results submitted by the teams.
<!-- TODO: repeat exclusion criteria -->
As discussed above, the analyses of only 30 teams out of all the submitted analysis were included in the meta-analytic model discussed here.
First, we report on the between-team variability estimate (i.e. the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), which is the focus of this study, followed by the meta-analytic estimate (i.e. the intercept of the meta-analytic model, in other words, the estimated effect of typicality on the acoustic production of adjective-noun combinations).
<!-- TR: remove reference to meta-analytical estimate -->

@@

<!-- TR: The meta analytical estimate is basically meaningless, given that the scale is not interpretable and artificial negative and positive estimates cancel each other out. I wonder whether we should take this out --> 
The meta-analytic intercept conflates estimates from a variety of responses taken from very different places in the utterance (nouns, adjectives, determiners, entire phrases or sentences, etc).
This means that some of the effects on a particular response as observed in a specific location within the utterance might naturally be positive, while other negative, resulting in a meta-analytic intercept of about zero.
We want to stress, however, that our focus is not on the meta-analytic intercept per se, but on the fact that a seemingly straightforward research question led to so many possible outcomes.
More on this in the Discussion section.

@@

While one might find it obvious that measuring different parts of the speech signal can lead to different results, the fact that analysts (and reviewer alike) considered all these data analytic pipelines valid ways of answering the same research question points to a lack of theoretical consensus on what parts of the speech signal correspond to what types of communicative functions. 
Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates: 
For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations. 
While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e. mean, min, max, or range) and how their statistical model was constructed (i.e. the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4). 
As shown by [-@breznau2021observing], even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.

@@

<!-- TODO: add LINK to credit -->
See image at LINK [for peer-review, see figure `credit-taxonomy.png` attached with submission].

>>>>

The project OSF repository contains all the materials mentioned in this paper and can be accessed at <https://osf.io/3bmcp/>.
The repository holds three main OSF components (`Data`, `Teams analyses` and `Questionnaires`), and a link to the project's GitHub repository.
The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.

@@

As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
The code is available at <https://many-speech-analyses.github.io/many_analyses/scripts/r/simulations/simulations>, Section 2.^[Cached model outputs can be found at <https://osf.io/wds2m/>.]
Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams. 
Thus in order to achieve our main goal, i.e. estimating variability among teams, we considered a minimum sample size of 10 teams as sufficient.
Given the exploratory nature of our study, however, we have sampled as many analysts as possible.
We received initial expressions of interest to participate from more than 200 analysts, though there was a substantial drop-out rate (see Section Results).

@@

The analysis teams registered for participation and each of the analysts individually answered a demographic and expertise questionnaire (`intake_form.pdf`).
A PDF version of this and all other questionnaires are available in the repository's `Questionnaires` component, at <https://osf.io/h6z8w/>.
The questionnaire collected information on the analysts' current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We then requested that they answer the research question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
To do so, they were given the data generated by the experiment described in Section [The data set](#s:dataset).
Data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
These can be found in the `Data` component at <https://osf.io/5agn9/>.

@@

Based on the common practices currently in place within the field, we anticipated that researchers would use multilevel regression models, thus common measurements of effect size, such as Cohen's $d$, might have been inappropriate.
Furthermore, @aczel2021 suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs. milliseconds for duration) which was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e. the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
Each \textsc{standardized model} was fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
Model refitting also constituted a way of validating the reported analyses, a step recommended by @aczel2021.
Details about the refitting procedure can be found at <https://many-speech-analyses.github.io/many_analyses/scripts/r/04_refit_workflow>.

@@

After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor in each reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
The outcome variable was the set of standardized effect sizes $\eta_i$.
The likelihood of $\eta_i$ was assumed to correspond to a normal distribution [@knight2000].
The analysis teams were entered as a group-level effect (i.e., `(1 | team)`, called *random effect* in the frequentist literature).
The standard errors $\text{se}_i$ were included as the standard deviation of $\eta_i$ to fit a measurement-error model, as discussed above.
We used regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\sigma_{\alpha_{\text{t}}}$ ($HalfCauchy(0, 1)$).
We fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
<!-- In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions. -->
The model did not incur any divergent transitions ($\hat{R}$ was not greater than 1) and the estimated sample sizes were sufficient.
The code used to run the model can be found at <https://many-speech-analyses.github.io/many_analyses/scripts/r/06_meta-analysis_prereg>.

@@

A normal distribution was used as the likelihood function of $\alpha_{t[i]}$.
The mean of $\alpha_{t[i]}$ was modeled on the basis of the overall intercept $\beta$ and on the coefficients of each predictor.
The numeric predictors were centered and scaled and the categorical predictors were sum coded.
We used a normal distribution with mean 0 and standard deviation 1 as the prior for the intercept and the predictors.
The model was run with the same settings as with the meta-analytic model.
The code used to run the model can be found at <https://many-speech-analyses.github.io/many_analyses/scripts/r/06_meta-analysis_prereg>.

@@

The initiating authors discussed the limitations, results, and implications of the study and collaborated with the analysts on writing the final manuscript for review as a stage-2 Registered Report.^[The comment history can be found at <https://docs.google.com/document/d/1CFgRo93mRgifpuFOuQE3vNBeMW-H7ps9eD--vxH-6CQ/edit?usp=sharing>.]

@@

The results section is divided into three parts.
We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
Second, we report the results of the meta-analytic model, focusing on between-team and between-model variability. 
<!-- and the estimated meta-analytic effect of word combination typicality on speech acoustics.-->
Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
The research compendium of the study, containing all the code and data presented here, can be found in the GitHub repository linked in the research compendium at <https://osf.io/3bmcp/>, in the `scripts/r/` folder.

@@

The question arises whether these unique analysis pipelines led to different conclusions. 
`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
Of the 104 submitted models, `r n_effects` were reported to show a statistically reliable effect (`r round(perc_effects,1)`%).

@@

This section deals with the meta-analytic analysis of the results submitted by the teams.
As discussed above, the analyses of only 30 teams out of all the submitted analysis were included in the meta-analytic model discussed here.
First, we report on the between-team variability estimate (i.e. the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), which is the focus of this study, followed by the meta-analytic estimate (i.e. the intercept of the meta-analytic model, in other words, the estimated effect of typicality on the acoustic production of adjective-noun combinations).

@@

The meta-analytic intercept conflates estimates from a variety of responses taken from very different places in the utterance (nouns, adjectives, determiners, entire phrases or sentences, etc).
This means that some of the effects on a particular response as observed in a specific location within the utterance might naturally be positive, while other negative, resulting in a meta-analytic intercept of about zero.
We want to stress, however, that our focus is not on the meta-analytic intercept per se, but on the fact that a seemingly straightforward research question led to so many possible outcomes.
More on this in the Discussion section.

@@

While one might find it obvious that measuring different parts of the speech signal can lead to different results, the fact that analysts (and reviewer alike) considered all these data analytic pipelines valid ways of answering the same research question points to a lack of theoretical consensus on what parts of the speech signal correspond to what types of communicative functions. 
Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates: 
For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations. 
While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e. mean, mininum, maximum, or range) and how their statistical model was constructed (i.e. the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4). 
As shown by [-@breznau2021observing], even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.

@@

See <https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy.png>.

### 2022-11-02 RR_manuscript/Draft_RR.tex
closes #260

The project OSF repository contains all the materials mentioned in this paper and can be accessed at \url{https://bit.ly/3AqU1ul}.
The repository holds three main OSF components (\texttt{Data}, \texttt{Teams\ analyses} and \texttt{Questionnaires}), and a link to the project's GitHub repository.
The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.

@@

As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect \emph{per se}.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from \citet{silberzahn2018many}.
The code is available at \url{https://many-speech-analyses.github.io/suppl/simulations.html}, Section 2.\footnote{Cached model outputs can be found at \url{https://bit.ly/3AgdHAN}.}
Variability among teams was operationalized as the standard deviation of the teams' reported effects from \citet{silberzahn2018many} (which we \emph{z}-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 \emph{z}-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
Thus in order to achieve our main goal, i.e.~estimating variability among teams, we considered a minimum sample size of 10 teams as sufficient.
Given the exploratory nature of our study, however, we have sampled as many analysts as possible.
We received initial expressions of interest to participate from more than 200 analysts, though there was a substantial drop-out rate (see Section Results).

@@

The analysis teams registered for participation and each of the analysts individually answered a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://bit.ly/3Cf3fdm}.
The questionnaire collected information on the analysts' current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We then requested that they answer the research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
To do so, they were given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
Data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
These can be found in the \texttt{Data} component at \url{https://bit.ly/3Ahawc7}.

@@

Based on the common practices currently in place within the field, we anticipated that researchers would use multilevel regression models, thus common measurements of effect size, such as Cohen's \(d\), might have been inappropriate.
Furthermore, \citet{aczel2021} suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs.~milliseconds for duration) which was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
Each \textsc{standardized model} was fitted as a Bayesian regression model with Stan \citep{stan2021}, RStan \citep{stan2020a}, and brms \citep{burkner2017} in R \citep{R-base}.
Model refitting also constituted a way of validating the reported analyses, a step recommended by \citet{aczel2021}.
Details about the refitting procedure can be found at LINK.

@@

After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor in each reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
The outcome variable was the set of standardized effect sizes \(\eta_i\).
The likelihood of \(\eta_i\) was assumed to correspond to a normal distribution \citep{knight2000}.
The analysis teams were entered as a group-level effect (i.e., \texttt{(1\ \textbar{}\ team)}, called \emph{random effect} in the frequentist literature).
The standard errors \(\text{se}_i\) were included as the standard deviation of \(\eta_i\) to fit a measurement-error model, as discussed above.
We used regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\) (\(HalfCauchy(0, 1)\)).
We fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
The model did not incur any divergent transitions (\(\hat{R}\) was not greater than 1) and the estimated sample sizes were sufficient.
The code used to run the model can be found at \textless\textgreater.

@@

A normal distribution was used as the likelihood function of \(\alpha_{t[i]}\).
The mean of \(\alpha_{t[i]}\) was modeled on the basis of the overall intercept \(\beta\) and on the coefficients of each predictor.
The numeric predictors were centered and scaled and the categorical predictors were sum coded.
We used a normal distribution with mean 0 and standard deviation 1 as the prior for the intercept and the predictors.
The model was run with the same settings as with the meta-analytic model.
The code used to run the model can be found at .

@@

The initiating authors discussed the limitations, results, and implications of the study and collaborated with the analysts on writing the final manuscript for review as a stage-2 Registered Report.

@@

The results section is divided into three parts.
We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
Second, we report the results of the meta-analytic model, focusing on between-team and between-model variability.
Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
The research compendium of the study, containing all the code and data presented here, can be found at \url{https://osf.io/3bmcp/}.

@@

Forty-six teams submitted their analyses by the established deadline.
Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
Of the analysis submitted by the 46 teams, the initiating authors identified analyses from 30 teams to be eligible to be included in the meta-analytic model.
Reasons for exclusion were: use of Generalised Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.

@@

While one might find it obvious that measuring different parts of the speech signal can lead to different results, the fact that analysts (and reviewer alike) considered all these data analytic pipelines valid ways of answering the same research question points to a lack of theoretical consensus on what parts of the speech signal correspond to what types of communicative functions.
Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates:
For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations.
While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, min, max, or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
As shown by \citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.

@@

See image at LINK {[}for peer-review, see figure \texttt{credit-taxonomy.png} attached with submission{]}.

>>>>

The project OSF repository contains all the materials mentioned in this paper and can be accessed at \url{https://osf.io/3bmcp/}.
The repository holds three main OSF components (\texttt{Data}, \texttt{Teams\ analyses} and \texttt{Questionnaires}), and a link to the project's GitHub repository.
The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.

@@

As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect \emph{per se}.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from \citet{silberzahn2018many}.
The code is available at \url{https://many-speech-analyses.github.io/many_analyses/scripts/r/simulations/simulations}, Section 2.\footnote{Cached model outputs can be found at \url{https://osf.io/wds2m/}.}
Variability among teams was operationalized as the standard deviation of the teams' reported effects from \citet{silberzahn2018many} (which we \emph{z}-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 \emph{z}-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
Thus in order to achieve our main goal, i.e.~estimating variability among teams, we considered a minimum sample size of 10 teams as sufficient.
Given the exploratory nature of our study, however, we have sampled as many analysts as possible.
We received initial expressions of interest to participate from more than 200 analysts, though there was a substantial drop-out rate (see Section Results).

@@

The analysis teams registered for participation and each of the analysts individually answered a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://osf.io/h6z8w/}.
The questionnaire collected information on the analysts' current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We then requested that they answer the research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
To do so, they were given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
Data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
These can be found in the \texttt{Data} component at \url{https://osf.io/5agn9/}.

@@

Based on the common practices currently in place within the field, we anticipated that researchers would use multilevel regression models, thus common measurements of effect size, such as Cohen's \(d\), might have been inappropriate.
Furthermore, \citet{aczel2021} suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs.~milliseconds for duration) which was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
Each \textsc{standardized model} was fitted as a Bayesian regression model with Stan \citep{stan2021}, RStan \citep{stan2020a}, and brms \citep{burkner2017} in R \citep{R-base}.
Model refitting also constituted a way of validating the reported analyses, a step recommended by \citet{aczel2021}.
Details about the refitting procedure can be found at \url{https://many-speech-analyses.github.io/many_analyses/scripts/r/04_refit_workflow}.

@@

After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor in each reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
The outcome variable was the set of standardized effect sizes \(\eta_i\).
The likelihood of \(\eta_i\) was assumed to correspond to a normal distribution \citep{knight2000}.
The analysis teams were entered as a group-level effect (i.e., \texttt{(1\ \textbar{}\ team)}, called \emph{random effect} in the frequentist literature).
The standard errors \(\text{se}_i\) were included as the standard deviation of \(\eta_i\) to fit a measurement-error model, as discussed above.
We used regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\) (\(HalfCauchy(0, 1)\)).
We fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
The model did not incur any divergent transitions (\(\hat{R}\) was not greater than 1) and the estimated sample sizes were sufficient.
The code used to run the model can be found at \url{https://many-speech-analyses.github.io/many_analyses/scripts/r/06_meta-analysis_prereg}.

@@

A normal distribution was used as the likelihood function of \(\alpha_{t[i]}\).
The mean of \(\alpha_{t[i]}\) was modeled on the basis of the overall intercept \(\beta\) and on the coefficients of each predictor.
The numeric predictors were centered and scaled and the categorical predictors were sum coded.
We used a normal distribution with mean 0 and standard deviation 1 as the prior for the intercept and the predictors.
The model was run with the same settings as with the meta-analytic model.
The code used to run the model can be found at \url{https://many-speech-analyses.github.io/many_analyses/scripts/r/06_meta-analysis_prereg}.

@@

The initiating authors discussed the limitations, results, and implications of the study and collaborated with the analysts on writing the final manuscript for review as a stage-2 Registered Report.\footnote{The comment history can be found at \url{https://docs.google.com/document/d/1CFgRo93mRgifpuFOuQE3vNBeMW-H7ps9eD--vxH-6CQ/edit?usp=sharing}.}

@@

The results section is divided into three parts.
We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
Second, we report the results of the meta-analytic model, focusing on between-team and between-model variability.
Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
The research compendium of the study, containing all the code and data presented here, can be found in the GitHub repository linked in the research compendium at \url{https://osf.io/3bmcp/}, in the \texttt{scripts/r/} folder.

@@

Forty-six teams submitted their analyses by the established deadline.
Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
Of the analysis submitted by the 46 teams, the initiating authors identified analyses from 30 teams to be eligible to be included in the meta-analytic model.
Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.

@@

While one might find it obvious that measuring different parts of the speech signal can lead to different results, the fact that analysts (and reviewer alike) considered all these data analytic pipelines valid ways of answering the same research question points to a lack of theoretical consensus on what parts of the speech signal correspond to what types of communicative functions.
Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates:
For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations.
While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, mininum, maximum, or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
As shown by \citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.

@@

See \url{https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy.png}.
